---
title: "Data"
output: html_notebook
editor_options:
  chunk_output_type: inline
---

# Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "#>",
                      collapse = TRUE)
knitr::opts_knit$set(root.dir = '../')
```

Data compiled and used in this project

## Data collection
We collect fecal samples of two primate and two bat species.

### Nyctalus noctula
Samples were collected by Lara Keicher, Dina Dechmann and colleagues during regular box monitoring at their field sites in Konstanz and Kreuzlingen.
Sample collection data was sent via email by Lara Keicher to Gisela on 30.4.2021 and is stored in `raw_data` as `Samples_Nycnoc_20210430.csv`.

```{r load Nycnoc sample collection data}
samplesNycnoc <- read.csv("vignettes/data/data_raw/Samples_Nycnoc_20210430.csv", header = TRUE, sep = ";", as.is = TRUE)

str(samplesNycnoc)


```

:::beware
Need to check sample IDs and include in table!
:::


## Data processing


---